Viscous Transport in Eroding Porous Media

### 2019-09-04 docs/transport/erosion_transport.tex
editing in section 6 of transport paper
add seven figures in section 4 & 6 of transport paper

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap} (a): The Delaunay triangulation of the porous media. 
(b): The distribution of gaps from (a).}
\end{figure}

@@

Finally, using network models for flow in porous media~\cite{}, the
anomalous dispersion rate can be linked to channel widths between solid
bodies.  We construct a Delaunay triangulation with the centers of the
eroding bodies corresponding to the vertices of the triangles.  Then, if
the side of a triangle connects two vertices, we call the bodies
neighbors.  Then, for each pair of neighbors, we measure the distance
between the bodies.  Once a Delaunay triangulation is formed, it is used
for all subsequent time steps until a body completely disappears.  At
this point, a new Delaunay triangulation is formed.

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var} (a): The mean of gaps with respect to porosity $\phi$.  
(b): The variance of gaps with respect to porosity $\phi$.}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_1}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_46}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_112}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_164}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_207}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_246}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_hist} The distribution of the gaps in the
case of erosion of 100 bodies at six porosities. (a) 100 bodies with 258 gaps as porosity $\phi = 50.09 \%$. 
(b) 100 bodies with 258 gaps as porosity $\phi = 55.02 \%$. 
(c) 97 bodies with 249 gaps as porosity $\phi = 65.03 \%$. 
(d) 92 bodies with 234 gaps as porosity $\phi = 75.14 \%$. 
(e) 75 bodies with 189 gaps as porosity $\phi = 85.07 \%$. 
(f)} 34 bodies with 74 gaps as porosity $\phi = 95.12 \%$. 
\end{figure}

>>>>

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap} (a): The Delaunay triangulation of the porous media. 
(b): The distribution of gaps from (a) with the fitting curve of Weibull distribution.}
\end{figure}

@@

Finally, using network models for flow in porous media~\cite{}, the
anomalous dispersion rate can be linked to channel widths between solid
bodies.  We construct a Delaunay triangulation with the centers of the
eroding bodies corresponding to the vertices of the triangles.  Then, if
the side of a triangle connects two vertices, we call the bodies
neighbors.  Then, for each pair of neighbors, we measure the distance
between the bodies.  Once a Delaunay triangulation is formed, it is used
for all subsequent time steps until a body completely disappears.  At
this point, a new Delaunay triangulation is formed. 
{\color{red}In Figure~\ref{fig:Eroding100gap_mean_var}, 
we record the gap distances between bodies neighbors and
calculate the mean and variance with respect to porosities. 
For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
which means the eroding . 
For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  }
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var} (a): The mean of gaps with respect to porosity $\phi$.  
(b): The variance of gaps with respect to porosity $\phi$.}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_1}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_46}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_112}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_164}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_207}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_246}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_hist} The distribution of the gaps in the
case of erosion of 100 bodies at six porosities and the fitting curves of Weibull distribution 
described by the shape parameter $k > 0$ and the scale parameter $\lambda > 0$. 
(a) 100 bodies with 258 gaps as porosity $\phi = 50.09 \%$ 
and $(k, \lambda)=(1 .4650, 0.0605)$ for Weibull distribution. 
(b) 100 bodies with 258 gaps as porosity $\phi = 55.02 \%$ 
and $(k, \lambda)=( 1.9485, 0.0737)$ for Weibull distribution. 
(c) 97 bodies with 249 gaps as porosity $\phi = 65.03 \%$ 
and $(k, \lambda)=( 2.5682, 0.0965)$ for Weibull distribution. 
(d) 92 bodies with 234 gaps as porosity $\phi = 75.14 \%$ 
and $(k, \lambda)=( 2.7771, 0.1255)$ for Weibull distribution. 
(e) 75 bodies with 189 gaps as porosity $\phi = 85.07 \%$ 
and $(k, \lambda)=( 2.6235, 0.1713)$ for Weibull distribution. 
(f) 34 bodies with 74 gaps as porosity $\phi = 95.12 \%$ 
and $(k, \lambda)=( 1.9840, 0.3194)$ for Weibull distribution. }
\end{figure}
